**Sequencing 16S rRNA gene fragments using the PacBio SMRT DNA sequencing system**

### 2016-01-30 Schloss_PacBio16S_PeerJ_2016.Rmd
Fix up R code in Conclusion

get_max_one_off <- function(region){
	max(as.numeric(rownames(one_offs[one_offs[,region]==1,])))
}
max_one_off <- sapply(regions, get_max_one_off)

```

@@

## Conclusions
The various sequencing platforms that are available to microbial ecologists are able to fill unique needs and have their own strengths and weaknesses. For sequencing the 16S rRNA gene, the 454 platform is able to generate a moderate number of high-quality 500-nt sequence fragments (error rates below 0.02%) {Schloss, 2011 #2466} and the MiSeq platform is able to generate a large number of high-quality 250-nt sequence fragments (error rates below 0.02%) {Kozich, 2013 #2719}. The promise of the PacBio sequencing platform was the generation of high-quality near full-length sequence fragments. As we have shown in this study, it is possible to generate near full-length sequences with error rates that are slightly higher, but comparable to the other platforms (i.e. `r round(100*pooled_error["V1V9","precluster"],2)`%). With the exception of the V4 region, the error rates were less than `r 100*max(pooled_error[!(rownames(pooled_error) %in% "V4"),"precluster"])`%. When we considered the shorter V4 region, which is similar in length to what is sequenced by the MiSeq platform, the error rates we observed with the PacBio platform were nearly 8-fold higher than what has previously been reported. It was unclear why these shorter reads had such a high error rate relative to the other regions. At this point, the primary limitation of generating full-length sequences on the PacBio platform is the cost of generating the data and accessibility to the sequencers.

>>>>

get_max_one_off <- function(region){
	max(as.numeric(rownames(one_offs[one_offs[,region]==1,])))
}
max_one_off <- sapply(regions, get_max_one_off)
```

@@

## Conclusions
The various sequencing platforms that are available to microbial ecologists are able to fill unique needs and have their own strengths and weaknesses. For sequencing the 16S rRNA gene, the 454 platform is able to generate a moderate number of high-quality 500-nt sequence fragments (error rates below 0.02%) {Schloss, 2011 #2466} and the MiSeq platform is able to generate a large number of high-quality 250-nt sequence fragments (error rates below 0.02%) {Kozich, 2013 #2719}. The promise of the PacBio sequencing platform was the generation of high-quality near full-length sequence fragments. As we have shown in this study, it is possible to generate near full-length sequences with error rates that are slightly higher, but comparable to the other platforms (i.e. `r round(error_summary[error_summary$region=="V1V9" & error_summary$method=="precluster","error"],2)`%). With the exception of the V4 region (`r round(error_summary[error_summary$region=="V4" & error_summary$method=="precluster","error"], 2)`%), the error rates were less than `r round(max(error_summary[error_summary$region!="V4" & error_summary$method=="precluster","error"]), 2)`%. When we considered the shorter V4 region, which is similar in length to what is sequenced by the MiSeq platform, the error rates we observed with the PacBio platform were nearly `r round(error_summary[error_summary$region=="V4" & error_summary$method=="precluster","error"]/0.02)`-fold higher than what has previously been reported on the other platforms. It was unclear why these shorter reads had such a high error rate relative to the other regions. At this point, the primary limitation of generating full-length sequences on the PacBio platform is the cost of generating the data and accessibility to the sequencers.
